---
title: "pain and suffering"
author: "rainer"
output: html_document
---

```{r}
library(rmarkdown)
library(reticulate)
source("module/Rscript.R")
pythonScript = source_python("module/pythonScript.py")
```

obj is a python class that stores information about a single object in the simulation. its instance variables are

id(string)
posx(float): the objects x coordinate
posy(float): y coordinate
dx(float): velocity along x axis
dy(float)
d2x(float): acceleration along xaxis)
d2y(float)
```{r}
obj000 = obj("000", 10,10,0,0,0,0)
obj001 = obj("001",1,1,1,1,1,1)
obj002 = obj("002",-20,12,0,0,0,0)
```

    
via functions from Rscript.R, we create a dataframe df that stores all the relevant info about the objects.
```{r}
createDf() #creates an empty dataframe
updateDf() #adds data from all the obj objects to df
```
    
    
main loop
```{r}
while (TRUE){
  makePlot() #visualize data stored in df. return ggplot object.
  for (i in obj$existing_objs){ #calculate the position of every obj instance for the next frame
    obj$updateObjA(i)
    obj$updateObjVP(i)
  }
  updateDf() #update df with all the updated data from the previous step
}
```


test: displaying objects
```{r}
x11()

library(jpeg)
img <- readJPEG("worm.jpg")
image(img)

```

